Improving Day Ahead Electricity Load Forecasts with Google Trends

### 2014-07-28 Paper/DraftPaper.Rnw
Abstract added.

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
Modern short term load forecasting has grown in analytically complexity and sophistication.  Day ahead forecasts now commonly use neural nets, Monte Carlo simulations and a wealth of historical data.  What they have not done is fully captured the sentiment and intentions of the people using the electricity.  This paper introduces Google Trend data, a summary of Google searches, as a way of capturing this sentiment and refining forecasts.  We show with drop all forward cross validation that this amendment decreases forecast uncertainty by approximately 5\% when compared to a statistically adjusted forecast and by over 50\% when compared to raw forecasts.
\end{abstract}
